\chapter{Projects related to the thesis}
\label{app:rel-projects}

\begin{itemize}
\item{\url{https://github.com/Soulou/msc-thesis-container-balancer-agent}\newline\vspace{1em}
The repository contains the code of the agent, which is running on every
hosting server, monitoring the host and its container in real time.}

\item{\url{https://github.com/Soulou/msc-thesis-container-balancer-controller}\newline\vspace{1em}
The controller of the infrastructure which finds the agents through
\textbf{Consul}. It manages the allocation and the load balancing operations in
the infrastructure.}

\item{\url{https://github.com/Soulou/msc-thesis-container-balancer-client}\newline\vspace{1em}
The client is a simple CLI tool to communicate with the controller. Otherwise
it would be necessary to write the HTTP requests by hand, which is not really
confortable.}

\item{\url{https://github.com/Soulou/msc-thesis-fibo-http-service}\newline\vspace{1em}
Webservice generating numbers of the fibonacci sequence. Used as a docker image
to generate load.}

\item{\url{https://github.com/Soulou/msc-thesis-memory-http-service}\newline\vspace{1em}
Webservice allocating a precise amount of memory during a precise duration,
used to simulate different kinds of webservices}

\item{\url{https://github.com/Soulou/msc-thesis-cpu-burn}\newline\vspace{1em}
Small software design to use completely a given amount of CPU cores.}

\item{\url{https://github.com/Soulou/msc-thesis-container-cpu-monitor}\newline\vspace{1em}
Tool to generate data about the consumption of each container run by
\textbf{Docker}.}

\item{\url{https://github.com/Soulou/msc-thesis-cloud-builder}\newline\vspace{1em}
Set of tools designed to deploy VMs automatically in an \textbf{OpenStack}
environment.}

\item{\url{https://github.com/Soulou/msc-thesis-ansible}\newline\vspace{1em}
\textbf{Ansible playbook to deploy everything required to run the exeperiment
on the VMs dpeloyed by the Cloud Builder.}}
\end{itemize}
