Operating system-level virtualization, commonly named containers, has taken an
important place in the current IT ecosystem.  They allow people to deploy
applications with an additional abstraction level. Whatever is the underlying
hardware, or the version of the operating system, a container will always run
the same way.

This technology has increased the flexibility of an infrastructure, and even
more of a cloud based infrastructure. Virtual Machines can be migrated and
containers also. This thesis defines a platform to test resource allocations
algorithms in a concrete environment, not a simulation. The scope of this work
has been reduced to bin packing algorithms which are the most common for
resource allocation and load balancing and only web applications have been used
for there ability to be stateless, and to migrate easily.

The defined platform is based on \textit{Docker} and on the decentralized
cluster management and service discovery tool \textit{Consul} and different
utilities have been developed to spawn containers gathered by services on the
different servers on the infrastructure.

Online bin packing and offline bin packing algorithms have been used to
respectively study the resource allocation and the load balancing problems
and experiments have been designed to measure their impact on the running
processes of the infrastructure.

\vspace{2em}
\textbf{Keywords}: operating system-level virtualization, containers, load
balancing, resource allocation, bin packing, cloud environment, virtual
machines, web applications
